---
title: "Stat433 HW 2"
author: "Annie Salcedo"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r flights}
library(dplyr)
library(nycflights13)
library(ggplot2)

flights
```

# 1) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r flights}
summary(flights)
flights %>% filter(is.na(dep_time))
```
8255 flights have a missing dep_time.
dep_delay, arr_time, arr_delay, and air_time are also missing.
these rows represent canceled flights, flights that never took off


# 2) Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r flights}
mutate(flights, dep_time = (dep_time %/% 100) * 60 + (dep_time %% 100), sched_dep_time = (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100))

```


# 3) Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
```{r flights}
flights %>% group_by(month, day) %>%
  summarize(avg_dep_delay = mean(dep_delay, na.rm = TRUE), prop_cancelled = sum(is.na(dep_time)/n()))  %>%
  ggplot(mapping = aes(x = avg_dep_delay, y = prop_cancelled)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)
  labs(x = "Delays per Day", y = "Proportion of Cancelled Flights per Day", title = "Average Delay vs Cancelled Flights")

```
